---
title: "Title"
author: 
  - Meryem Şahan[^1]
bibliography: ../bibliography/biblio.bib
csl: ../csl/apa.csl
header-includes:
  - \usepackage{polyglossia}
  - \setmainlanguage{english}
  - \usepackage{booktabs}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=10pt}
output:
  bookdown::pdf_document2:
    fig_caption: yes
    fig_height: 3
    fig_width: 4
    keep_tex: no
    latex_engine: xelatex
    number_sections: yes
    toc: no
geometry: margin=1in
link-citations: yes
urlcolor: blue
fontsize: 12pt
biblio-style: apalike
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE, echo = TRUE, message = FALSE, warning = FALSE)
```

<!-- ======================================================================= -->
<!-- ============================== FOOTNOTES ============================== -->
<!-- ======================================================================= -->
[^1]: 21080515, [Github Repo](https://github.com/MeryemSahan/Midterm.git)




# Introduction
[@kim2019comparing]
deneme 1

@SHEN201117


Shen et al. (2011)  conducted a comparative analysis of urban sustainability indicators used in different practices, proposing a comparative basis to guide the selection of indicators for sustainable urbanization plans.

@haghshenas2012urban

## Literature Review


deneme deneme deneme 

#Data Retrival
I have received my data using World Bank's special package for R. Code chunks are not shown in the pdf file but it is available in r project.

```{r GDP Growth Rate, eval=FALSE, cache=TRUE, include=FALSE}
library(WDI)
countries <- c("EG", "TR", "AU", "IN", "IR", "CA", "KE", "IQ", "DK", "NG", "MX", "DE", "PK", "RO", "IL", "LK", "BR", "NZ", "GH", "BG", "SE", "ID", "LY", "US", "BD", "MU", "JP", "RU", "KR")
start_year <- 2010
end_year <- 2020
indicator <- "NY.GDP.MKTP.KD.ZG"
gdp_growthrate_data <- WDI(country = countries, indicator = indicator, start = start_year, end = end_year)
"
 file_path <- "C:/Users/Meryem/Desktop/Proposal/data/gdp_growthrate_data.csv"
write.csv(gdp_growthrate_data, file = file_path, row.names = FALSE)


```

```{r World Governance Indicators, eval=FALSE, cache=TRUE, include=FALSE}
indicators <- c("RQ.EST", "VA.EST", "PV.EST", "GE.EST", "CC.EST", "RL.EST")
wgi_data <- WDI(country = countries, indicator = indicators, start = start_year, end = end_year)
 file_path <- "C:/Users/Meryem/Desktop/Proposal/data/wgi_data.csv"
 
write.csv(wgi_data, file = file_path, row.names = FALSE)
```

```{r GDP per capita, eval=FALSE, cache=TRUE, include=FALSE}
indicator <- "NY.GDP.PCAP.KD"
gdpcap_data <- WDI(country = countries, indicator = indicator, start = start_year, end = end_year)
file_path <- "C:/Users/Meryem/Desktop/Proposal/data/gdpcap_data.csv"
write.csv(gdpcap_data, file = file_path, row.names = FALSE)

```


```{r Trade (% of GDP), eval=FALSE, cache=TRUE, include=FALSE, echo=FALSE}
indicator <- "NE.TRD.GNFS.ZS"
trade_data <-  WDI(country = countries, indicator = indicator, start = start_year, end = end_year)
file_path <- "C:/Users/Meryem/Desktop/Proposal/data/trade_data.csv"
write.csv(trade_data, file = file_path, row.names = FALSE)

```


```{r Foreign direct investment, eval=FALSE, include=FALSE, cache=TRUE, echo=FALSE}
indicator <- "BX.KLT.DINV.WD.GD.ZS"
fdi_data <-  WDI(country = countries, indicator = indicator, start = start_year, end = end_year)
file_path <- "C:/Users/Meryem/Desktop/Proposal/data/fdi_data.csv"
write.csv(fdi_data, file = file_path, row.names = FALSE)

```


```{r Labor Force, eval=FALSE, include=FALSE, cache=TRUE, echo=FALSE}
indicator <- "SL.TLF.TOTL.IN"
lab_data <-  WDI(country = countries, indicator = indicator, start = start_year, end = end_year)
file_path <- "C:/Users/Meryem/Desktop/Proposal/data/fdi_data.csv"
write.csv(lab_data, file = file_path, row.names = FALSE)

```


```{r Education Expenditure, eval=FALSE, cache=TRUE, include=FALSE, echo=FALSE}
indicator <- "SE.XPD.TOTL.GD.ZS"
ed_data <- WDI(country = countries, indicator = indicator, start = start_year, end = end_year)
file_path <- "C:/Users/Meryem/Desktop/Proposal/data/ed_data.csv"
write.csv(ed_data, file = file_path, row.names = FALSE)
```

```{r Gini Coefficent, eval=FALSE, cache=TRUE, include=FALSE, echo=FALSE}
indicator <- "SI.POV.GINI"
gini_data <- WDI(country = countries, indicator = indicator, start = start_year, end = end_year)

file_path <- "C:/Users/Meryem/Desktop/Proposal/data/gini_data.csv"
write.csv(gini_data, file= file_path, row.names = FALSE)

```


\newpage
# References {#references}
<div id="refs"></div>

